RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
added comment about the need, perhaps, for an add_taxa method
typo fix

NeXML files can also be built up bit by bit using the `add_characters`,
`add_trees`, and `add_meta`.  Each of these functions can add data to an
existing `nexml` object or create a new nexml object if none is provided.
Here we first create a `nexml` object containing the phylogeny data,
and then add the character data to it:

@@

At the heart of the NeXML standard is the ability to encode arbitrary
metadata in precisely specified, machine-readable formats that maintain
backwards compabitibilty with any existing NeXML parser. NeXML uses the
"Resource Description Framework in Annotations", or RDFa,
as described in @Vos_2012.  These annotations can be used to add 
information to any particular element of the data, (a tree, node, edge,
or taxonomic unit; a character matrix or specific trait, or even another 
metadata annotation or the NeXML data file as a whole). `RNeXML` provides
a range of tools for accessing metadata embedded in a NeXML file.

>>>>

<!-- how about add_taxa? -->
NeXML files can also be built up bit by bit using the `add_characters`,
`add_trees`, and `add_meta`.  Each of these functions can add data to an
existing `nexml` object or create a new nexml object if none is provided.
Here we first create a `nexml` object containing the phylogeny data,
and then add the character data to it:

@@

At the heart of the NeXML standard is the ability to encode arbitrary
metadata in precisely specified, machine-readable formats that maintain
backwards compatibility with any existing NeXML parser. NeXML uses the
"Resource Description Framework in Annotations", or RDFa,
as described in @Vos_2012.  These annotations can be used to add 
information to any particular element of the data, (a tree, node, edge,
or taxonomic unit; a character matrix or specific trait, or even another 
metadata annotation or the NeXML data file as a whole). `RNeXML` provides
a range of tools for accessing metadata embedded in a NeXML file.
